---
title: "Assignment 4"
author: Liang-Cheng, Chen
output:
  pdf_document: default
  html_notebook:
    highlight: zenburn
    theme: united
  html_document:
    df_print: paged
---


### Package & Data

Import the `ergm` package and its dataset `florentine`.

```{r message=FALSE}
library(ergm)
library(stargazer) # for showing result table
data(florentine)
```

data overview

```{r}
flomarriage
```



### Problem 1

Estimate ERGM for flomarriage network data with absolute difference in wealth, #edges, #triangles.

```{r message=FALSE, warning=FALSE}
model.baseline <- ergm(flomarriage ~ edges + triangle)
model.1 <- ergm(flomarriage ~ edges + triangle + absdiff("wealth"))
summary(model.1)
```


### Problem 2

First, count how many 2-stars, 3-stars seperately.

From the result we get there are __47 2-stars__ and __34 3-stars__.

```{r}
summary(flomarriage ~ kstar(2:3))
```

Second, estimate the model with `kstar(2:3)`, num of edges.

```{r message=FALSE, warning=FALSE}
model.2 <- ergm(flomarriage ~ edges + kstar(2:3))
summary(model.2)
```

Comparing 2 models,

(1) Model 1 shows that number of edges, difference in family wealth are significant.
    
(2) After adding number of 2-stars and 3-stars, the number edges becomes insignificant.

(3) The BIC is smaller in model 1. (The smaller the better.)
    

```{r message=FALSE, warning=FALSE}
stargazer(model.baseline, model.1, model.2, type = 'text')
```





