---
title: "Econ 7217 Assignment 3"
output: 
  github_document:
    html_preview: true
    dev: jpeg
  html_notebook:
    theme: spacelab
    highlight: tango
---


## packages and data

```{r message=FALSE, warning=FALSE}
library(ergm)
library(sna)
library(latentnet)
library(network)

load('../data/dataset_ergmm.RData')

```


## Problem 1

Change the latent position model option from distance model to projection model.

Here, using `bilinear()` instead of `euclidean()` inside `ergmm` function.


```{r}
model_1 <- ergmm(net ~ bilinear(d = 2), 
                 control=ergmm.control(burnin=100000,sample.size= 10000,interval=5))
```

### Estimation

The result summary was stated:

```{r message=FALSE}
summary(model_1)
```

### Graph

The graphic result:

```{r message=FALSE, warning=FALSE}
plot(model_1, pie = T, main = 'Projection Model (Inner Product)', print.formula = F)
```

## Question 2

Instead of using 2 groups, set the cluster-group number to 3.

```{r message=FALSE, warning=FALSE}
model_2_fomula <- formula(net ~ nodematch("white") + nodematch("male") + euclidean(d=2, G=3))


model_2 <- ergmm(model_2_fomula,
                control=ergmm.control(burnin=100000,sample.size= 10000,interval=5))

```

### Estimation

The result summary shows that the male factpr is significant.

```{r}
summary(model_2)
```

### Graph

As the figure shown, there are 3 groups (blocks) denoted by 3 circles with different colors.

```{r warning=FALSE}
plot(model_2, pie = T, main = "Cluster = 3", print.formula = F)
```



## P.S. Comparing to demo code setting

```{r message=FALSE, warning=FALSE}
model1_fomula <- formula(net ~ euclidean(d=2))

model1 <- ergmm(model1_fomula,
                control=ergmm.control(burnin=100000,sample.size= 10000,interval=5))

model2_fomula <- formula(net ~ nodematch("white") + nodematch("male") +
                               euclidean(d=2,G=2))
model2 <- ergmm(model2_fomula,
                control=ergmm.control(burnin=100000,sample.size= 10000,interval=5))


```

### Model 1
```{r warning=FALSE}
par(mfrow=c(1,2))
plot(model1, pie = T, main = "Distance", vertex.cex = 2.5, print.formula = F)
plot(model_1, pie = T, main = "Projection",  vertex.cex = 2.5, print.formula = F)

```

### Model 2

There is a problem that although using distance makes |z1 - z2| = |z2 - z1|, 
which makes the result is invariant through the sign of z.

But as the figure below shown, my question is will the latent variable position of nodes change,
with only the cluster number is different?

```{r warning=FALSE}
par(mfrow=c(1,2))
plot(model2, pie = T, main = "Cluster = 2", vertex.cex = 2.5, print.formula = F)
plot(model_2, pie = T, main = "Cluster = 3",  vertex.cex = 2.5, print.formula = F)

```




